JMS

### 2021-04-28 analysis.Rmd
del exposure index scatterplot

library(knitr)
library(ggplot2)
library(reshape)
library(reshape2)
library(forcats)
library(tidyr)
library(dplyr)
library(gtable)
library(kableExtra)
library(magick)
library(webshot)
library(xtable)
library(gridExtra)
library(ggrepel)
library(viridis)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
webshot::install_phantomjs()

@@

# Add working directory, substitute * in quotes (leave "/" for folders output of images and latex, or tweak). If bug with output name "images/" or "latex/", delete them in the name of output

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/")

@@

basic <- read.csv("df_basic.csv",sep =",")                 # basic condition
value_basic <- read.csv("df_valuebasic.csv",sep = ",")     # value basic
asym_dom <- read.csv("df_asym_dom.csv",sep = ",")          # asymmetric conditions, baseline figure dominant preference
dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals
sa_asym <- read.csv("df_sa_asym.csv",sep =",")             # sensitivity analysis, ethnic asymmetry
etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
asym_all <- read.csv("df_asym_all.csv",sep =",")           # baseline ethnic  asymmetry

@@

circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
names(circle_orange.labs) <- c("20","50","80")

@@

# database filter
excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))

plotname <- "images/vllblc.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal local"

# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
#        dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
# 
#  expo_pic <-   ggplot(data = dataset_sa) + 
#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
#

@@

# database filter
excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))

@@

plotname <- "images/vllbmn.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal minority"

# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
       # dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)

# ethnic exposure plot

#  expo_pic <-   ggplot(data = dataset_sa) + 
#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

# database filter
excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
etlib_df <- etlib[!excl] %>% filter(eth_lib_min  == 0)  %>% 
group_by(eth_lib_loc,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))

plotname <- "images/et_libloc.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal local"

@@

# database filter
excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_loc) %>% summarise_all(c("mean"= mean,"sd"= sd))

plotname <- "images/et_libmin.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal minority"

@@

xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)

 expo_pic <-   ggplot(data = dataset_sa) + 
  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +

   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +

    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +

  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
   xlab(expression(Exposure[correct])) + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

#, plot.caption = element_text(hjust= 0.5, size = 11)
ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))

@@

df_vllblc50 <- dataset_sa %>%  filter(circle_orange == 50)
tablerb_prox50 <- xtable(df_vllblc50[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox50,type = "latex", file = "latex/vllblc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

df_vllblc20 <- dataset_sa %>%  filter(circle_orange == 20)
tablerb_prox20 <- xtable(df_vllblc20[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox20,type = "latex", file = "latex/vllblc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

df_vllblc80 <- dataset_sa %>%  filter(circle_orange == 80)
tablerb_prox80 <- xtable(df_vllblc80[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox80,type = "latex", file = "latex/vllblc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

>>>>

library(knitr)
library(ggplot2)
library(reshape)
library(reshape2)
library(forcats)
library(tidyr)
library(dplyr)
library(gtable)
library(kableExtra)
library(magick)
library(webshot)
library(xtable)
library(gridExtra)
library(ggrepel)
library(viridis)
library(data.table)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
webshot::install_phantomjs()

@@

# Set workind directory
setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/")

@@

basic <- read.csv("df_basic.csv",sep =",")                 # basic condition
value_basic <- read.csv("df_valuebasic.csv",sep = ",")     # value basic
asym_dom <- read.csv("df_asym_dom.csv",sep = ",")          # asymmetric conditions, baseline figure dominant preference
dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals, sensitivity analysis, ethnic asymmetry
# etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
asym_all <- read.csv("df_asym_all.csv",sep =",")           # baseline ethnic  asymmetry
# sa_asym <- read.csv("df_sa_asym.csv",sep =",")  #  PREVIOUS version is saved on GITHUB !! CHECK IF WORTH IT

# Checked for 90!
sa_asym <- read.csv("sa_asym_90.csv",sep =",")      
etlib <- read.csv("etlib_90.csv",sep =",")

# dfloc <- read.csv("test_90/etlib_loc.csv",sep = ",", skip = 6)
# dfmin <- read.csv("test_90/etlib_min.csv",sep = ",", skip = 6)
# names(dfloc) <- pull(read.csv("test_90/legend_90.csv"))
# names(dfmin) <- pull(read.csv("test_90/legend_90.csv"))
# etlib <- select(etlib, - c(32:47))
# IDloc <- "etlib_loc"
# IDmn <- "etlib_min"
# dfloc <- cbind(IDloc,dfloc)
# dfmin <- cbind(IDmn,dfmin)
# names(dfmin)[names(dfmin) == "IDmn"] <- "ID"
# etlib <- rbind(etlib,dfmin)
# write.csv(etlib,"etlib_90.csv",row.names=FALSE)

@@

circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority","10% liberal minority","90% liberal minority")
names(circle_orange.labs) <- c("20","50","80","10","90")

@@

# database filter
sa_asym <- sa_asym %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)
excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))

plotname <- "vllblc.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal local"

@@

# database filter
sa_asym <- sa_asym %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)
excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))

@@

plotname <- "vllbmn.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal minority"

@@

# database filter
etlib <- etlib %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)

plotname <- "et_libloc.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal local"

@@

# database filter
etlib <- etlib %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)

excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_loc) %>% summarise_all(c("mean"= mean,"sd"= sd))

plotname <- "et_libmin.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal minority"

@@

@@

@@

df_vllblc50 <- dataset_sa %>%  filter(circle_orange == 50)
tablerb_prox50 <- xtable(df_vllblc50[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox50,type = "latex", file = "vllblc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

df_vllblc10 <- dataset_sa %>%  filter(circle_orange == 10)
tablerb_prox10 <- xtable(df_vllblc10[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox10) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $10 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox10,type = "latex", file = "vllblc10.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

df_vllblc90 <- dataset_sa %>%  filter(circle_orange == 90)
tablerb_prox90 <- xtable(df_vllblc90[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox90) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $90 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
print(tablerb_prox90,type = "latex", file = "vllblc90.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
